Telemetry Module for Solar Vehicle

### 2021-06-07 documentation/FinalPaper/paper.tex

\title{Bare Demo of IEEEtran.cls\\ for IEEE Journals}

\author{\IEEEauthorblockN{Victor Alexander Hansen}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{Steffan Martin Kunoy}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{Tjark Petersen}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}}
%\author{Victor Alexander Hansen, Steffan Martin Kunoy, Tjark Petersen}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
The abstract goes here.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
IEEE
\end{IEEEkeywords}

\section{Introduction}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by the IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{T}{his} demo file is intended to serve as a ``starter file''
for IEEE journal papers produced under \LaTeX\ using
IEEEtran.cls version 1.8b and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.

\hfill mds

\hfill August 26, 2015

\subsection{Subsection Heading Here}
Subsection text here.

% needed in second column of first page if using \IEEEpubid
%\IEEEpubidadjcol

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

@@

% if have a single appendix:
%\appendix[Proof of the Zonklar Equations]
% or
%\appendix  % for no appendix heading
% do not use \section anymore after \appendix, only \section*
% is possibly needed

% use appendices with more than one appendix
% then use \section to start each appendix
% you must declare a \section before using any
% \subsection or using \label (\appendices by itself
% starts a section numbered zero.)
%

\appendices
\section{Proof of the First Zonklar Equation}
Appendix one text goes here.

% you can choose not to have a title for an appendix
% if you want by leaving the argument blank
\section{}
Appendix two text goes here.

@@

The authors would like to thank...

@@

>>>>

\title{Telemetry Module for Solar Vehicle}

\author{\IEEEauthorblockN{Victor Alexander Hansen s194027, Steffan Martin Kunoy s194006, Tjark Petersen, s186083}
\IEEEauthorblockA{\textit{Department of Electrical Engineering} \\
\textit{Technical Uniservity of Denmark}\\
Kongens Lyngby, Denmark \\
31015 Introductory project - electrotechnology\\
s194027@student.dtu.dk, s194006@student.dtu.dk, s186083@student.dtu.dk}}
%\author{Victor Alexander Hansen, Steffan Martin Kunoy, Tjark Petersen}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
Abstract
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
ROAST, telemetry, CAN
\end{IEEEkeywords}

\section{Introduction}

\IEEEPARstart{I}{n} 2023, DTU Roadrunners Solar Team, abbreviated ROAST, is set to participate in the Bridgestone World Solar Challenge, a race spanning over 3000 km across Australia from Darwin in Northern Territory to Adelaide in South Australia. The solar car have limited opportunities for recharging during the race, so the main source of energy during the race, is from solar energy. To this end, solar panels will cover the car, however, the solar car is only allowed to have a maximum of 4 square meters of solar panels. This emphasizes the need to create an energy-efficient solar car to win the race \cite{wsc}.\\
Throughout the race the solar car will be monitored by a support car, which can monitor the car's condition and issue commands. This is a crucial function as the solar car will be navigating Australia's busy highways, where the heat and tire pressure may cause a detriment to the vehicle. The support car will therefore be able to analyze and react to the data stream being transmitted from the solar car, even when the driver is preoccupied by driving the car and navigating traffic. \\
The main function of the telemetry module is to read data from the solar car's on-board CAN (Controller Area Network) bus and transmit it via an RF-transceiver to the support car, while simultaneously logging data locally in a "black box" memory chip. The support car is equipped with a similar module such that the support crew can react to the data manually or automatically by sending commands back to the CAN bus. As a consequence, the telemetry module plays a vital role in the communication between both vehicles, considering the distance between them may be up to 1 km depending on traffic conditions.\\
Therefore, the telemetry module must both serve the purpose of fulfilling the necessary specifications for communication, while also being as energy-efficient as possible. The project will mainly focus on the former that is, ensuring that the module meets the specifications with a solid solution.

\subsection{Problem Statement}
Remote sensing of data from the solar car will give the ROAST team a competitive advantage as the support vehicle will take on a more active role in controlling and optimising the car's performance. This will ease the burden on the driver and engage a large part of the supporting crew. For these reasons we have chosen to focus our project on the following points:   
\begin{itemize}
    \item How can we design a module that can read and write sensor data and commands from a CAN bus network? 
    \item How can CAN data be transmitted securely over a distance of up to one kilometer?
    \item How does the support-car module process data upon receiving it from the solar car?
    \item What is the best method for storing data locally (black box) while being accessible at a later time?
    \item How can the CAN data be made accessible for further processing in e.g. Matlab?
\end{itemize}

\section{Methodology}
Sprint method and verification of software
\section{Design}
\begin{itemize}
    \item Block diagram
    \item Components
    \item Software stack
    \item Final design
\end{itemize}
\subsection{CAN} % Victor
\subsection{nRF24 \& Shockburst} % Steffan 
\subsection{Message protocol}

\section{Implementation}

\subsection{Solar Car} 
\subsubsection{Black Box} % tjark
\subsubsection{CAN transceiver}
\subsection{Support Vehicle}
\subsubsection{GUI} % tjark
\subsubsection{RF transceiver}

\section{Verification} % Victor
Throughout the project we have used the cross-platform IDE PlatformIO, which is a development platform for embedded systems. This has greatly increased the efficiency in our work due to the

\section{Discussion}

@@

@@

The authors would like to thank Christian Kampp Kruse for his assistance as coordinator for this project. The authors would also like to thank Claus from DTU Mekanik % Udbedr

@@

\section{References}
\begingroup
\renewcommand{\section}[2]{}%
%\renewcommand{\chapter}[2]{}% for other classes
\begin{thebibliography}{}
\bibitem{wsc}
Bridgestone World Solar Challenge, 
URL: https://worldsolarchallenge.org/
\bibitem{ROAST}
Reports and source files provided by DTU ROAST
\bibitem{teensy}
Teensy microcontroller,
URL: https://www.pjrc.com/teensy/
\bibitem{C++}
Website for learning C++
https://www.learn-cpp.org/
\end{thebibliography}
\endgroup
